\documentclass{article}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{bbm}
\usepackage{fancyhdr}
% \usepackage{listings}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{courier}
\usepackage[pdftex,colorlinks=true, urlcolor = blue]{hyperref}
\usepackage{pdfpages}


\oddsidemargin 0in \evensidemargin 0in
\topmargin -0.5in \headheight 0.25in \headsep 0.25in
\textwidth 6.5in \textheight 9in
\parskip 6pt \parindent 0in \footskip 20pt

% set the header up
\fancyhead{}
\fancyhead[L]{Stanford Aeronautics \& Astronautics}
\fancyhead[R]{Fall 2020}

%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand\headrulewidth{0.4pt}
\setlength\headheight{15pt}

\usepackage{xparse}
\NewDocumentCommand{\codeword}{v}{%
\texttt{\textcolor{blue}{#1}}%
}

\usepackage{xcolor}
\setlength{\parindent}{0in}

\title{AA 274A: Principles of Robot Autonomy I \\ Problem Set 2}
\author{Name: Li Quan Khoo     \\ SUID: lqkhoo (06154100)}
\date{\today}

\begin{document}

\maketitle
\pagestyle{fancy} 

\section*{Problem 1: Camera Calibration}
\begin{enumerate}[label=(\roman*)]
\item % (i)
(code)

\item % (ii)
(code)

\item % (iii)
(code)

\item % (iv)
(code)

\item % (v)
(code)

\end{enumerate}


\section*{Problem 2: Line Extraction}
\begin{enumerate}[label=(\roman*)]
\item % (i)
(code)

\item % (ii)
TODO

\end{enumerate}


\section*{Problem 3: Linear Filtering}
\begin{enumerate}[label=(\roman*)]
\item % (i)

\begin{enumerate}
	\item
	\begin{equation}
	F = \begin{bmatrix}
	1 & 2 & 3 \\
	4 & 5 & 6 \\
	7 & 8 & 9
	\end{bmatrix}
	\end{equation}
	
	\item
	\begin{equation}
	F = \begin{bmatrix}
	2 & 3 & 0 \\
	5 & 6 & 0 \\
	8 & 9 & 0
	\end{bmatrix}
	\end{equation}
	
	\item
	This kernel is doing discrete difference (differentiation) of the image along the horizontal axis. It could be used to perform edge detection tasks.
	\begin{equation}
	F = \begin{bmatrix}
	2 & 2 & -2 \\
	5 & 2 & -5 \\
	8 & 2 & -8
	\end{bmatrix}
	\end{equation}
	
	\item
	This is an isotropic, normalized Gaussian kernel performing blurring on the image. It could be used to filter out high frequency information on either axis.
	\begin{equation}
	F = \frac{1}{16}\begin{bmatrix}
	21 & 36 & 33 \\
	52 & 80 & 68 \\
	57 & 84 & 69
	\end{bmatrix}
	\end{equation}
	
	
	
\end{enumerate}

\item % (ii)
I'm assuming that the question is alluding to the fact that performing correlation (or convolution) over an input of depth $d$ means we end up summing over $d$ individual correlations or convolutions performed on individual input channels.

This is saying that:

\begin{equation}
G(i,j) = \sum_{w} \Bigg( \sum_{u}\sum_{v} F_w(u,v) \cdot I_w(i+u,j+v) \Bigg)
\end{equation}
where $G(i,j)$ is a correlation operation at position $i,j$ of the image, and $F$ and $I$ are flattened vector representations of the kernel and current image patch (including padding) that we are operating over. Therefore, writing out the matrices explicitly:

\begin{equation}
G(i,j) = \sum_w
\begin{bmatrix}- & F_w^\mathsf{T}(u,v) & -\end{bmatrix}
\begin{bmatrix}| \\ I_w \\ |\end{bmatrix}
\end{equation}

which is of course equal to taking the dot product of $f$, which is a single big vector f of length $u\cdot v\cdot w$ with a single big vector $t(i,j)$ of length $u\cdot v\cdot w$ as expressed below:

\begin{equation}
G(i,j) = 
\begin{bmatrix}F_1^\mathsf{T} & \hdots & F_w^\mathsf{T}\end{bmatrix}
\begin{bmatrix}I_{1} \\ \vdots \\ I_{w}\end{bmatrix}
= f^\mathsf{T} t_{i,j}
\end{equation}

\item % (iii)
(code)

\item % (iv)
TODO report runtime.

To answer the first hint, no it does not. For a mono-channel image, each individual patch could be flattened and stacked into a $u\cdot v$ by $h\cdot w$ array and processed in parallel.

To answer the second hint, the total number of addmul operations are $u \cdot v \cdot w \cdot h$ as we are applying a filter with a receptive field of $u$ by $v$ over a single-channel input of size $w$ by $h$. If the filter could be expressed as an outer product, the total cost would be $(u+v) \cdot w \cdot h$.

Lastly, we could implement Winograd's minimal filtering algorithm that pre-computes intermediate values that depend only on kernel weights with the motivation of saving redundant computation.


\item % (v)
We use the result that any $m\times n$ matrix of rank 1 could be expressed as a vector outer product $uv^\mathsf{T}$. This is obvious, because the column rank of any vector $u$ has to be equal to 1. To answer the question, if we know that a matrix is rank 1 and we simply wish to recover $u$ and $v^\mathsf{T}$, these correspond to the orthogonal matrices after performing SVD on the original matrix. Alternatively, $u$ could be any of its columns and $v$ is the single nonzero row left over after performing Gaussian elimination, up to a constant factor $k$.

Additionally, it is easy to see that for any $m\times n$ matrix of rank $r$, we can express it as a linear combination of $r$ matrices, which themselves could be expressed as the outer product of the linearly independent rows and columns of the original matrix. This is a generalization of the above result.

\item % (vi)
(code)

\item % (vii)
Convolution with a flipped filter in all its dimensions would produce the same output as correlation with an unmodified filter.

In other words,
\begin{equation}
G(i,j) = \sum_{u=1}^k\sum_{v=1}^l F(u,v)\cdot I(i-u, j-v)
= \sum_{u=1}^k\sum_{v=1}^l F(k-u, l-v) \cdot I(i+u, j+v)
\end{equation}


	
\end{enumerate}


\section*{Problem 4: Template Matching}
\begin{enumerate}[label=(\roman*)]
\item % (i)
(code)

\item % (ii)
(code)

\item % (iii)
TODO
	
\end{enumerate}


\section*{Problem 5: Stop Sign Detection and FSM in ROS}
\begin{enumerate}[label=(\roman*)]
\item % (i)
TODO

\item % (ii)
(code)

\item % (iii)
TODO

\item % (iv)
TODO

\item % (v)
null

\item % (vi)
TODO

\item % (vii)
(code)

\item % (viii)
TODO
	
\end{enumerate}

\section*{Extra Problem: Image Pyramids}
\begin{enumerate}[label=(\roman*)]
\item % (i)
(code)

\item % (ii)
TODO

\item % (iii)
(code)

\item % (iv)
TODO

\item % (v)
(code)

\item % (vi)
TODO

\item % (vii)
(code)

\item % (viii)
(code)

\item % (xi)
TODO

\end{enumerate}

\end{document}
